### 2019-04-22 monograph/thesis/chapters/introduction.tex
Fully inserted \lang tags on introduction.tex and motivation.tex

\lang{
    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.
}{
    A \hyperref[sec:primeira_parte]{primeira parte} deste trabalho será baseado em artigos,
    livros, outras dissertações,
    sites confiáveis e por novas evidências demonstradas no desenvolvimento deste trabalho.
}

\lang{
    In this proposal last chapter which lies on the part
    called `\nameref{sec:segunda_parte}', which holds the implementation of a
    tool for code `Beautifying'.
}{
    E finalmente,
    na \hyperref[sec:segunda_parte]{segunda parte} deste trabalho,
    será apresentada a sugestão e implementação de uma ferramenta.
}

@@

\lang{
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}
}{
    Perguntas como ``O quê são boas práticas de programação'' não são fáceis de responder.
    Cada programador aprende a escrever seu códigos de uma determinada maneira,
    seja utilizando 2, 4,
    ou 8 espaços para criar blocos de indentação,
    ou sempre deixar uma linha em branco antes de estruturas de controle como if\s,
    while\s, etc. \cite{naturalCodingConventions}
}

But entering the universe of good practices, there are many things for
discoursing. Nonetheless, in this work is presented the implementation of
tool called `Object Beautifier', which specifically dedicates on how to
perform the best layout/display of programming code on the computer screen,
so that maximize and facilitate the understanding of same
\cite{automaticSynthesis}.
Therefore, allowing the programmer to disperse
more time and efforts thinking about its coding algorithms problem,
other than trying to decipher the information that is presented
to it on the screen through infinit different code layouts
\cite{usingVersionControlData}.

Within this work\s area, we need to also think long and hard about how to
share the programming code of the programmers among you. Now, the problem of
human diversity, like all big scientific questions -- how do you explain
something like that -- It can be broken down into sub-questions. It happens
many times, which is a good practice for a `Programmer A', is not the same
to another `Programmer B'. For example, imagine some code where a programmer
decided to put before each `if' statement, a blank line. It is therefore
expected that whenever we see a blank line we can potentially find a
matching `if', which can be considered a quite useful pattern matching as
empty line may call better your attention. \cite{aPrettyGoodFormatting}

But again this is something heavily dependent of what each one learning
through their life time. Imagine another programmer do not liked this rule,
and when he was writing your code involving an `if', he did not put such
blank line another programmer is expecting. So when the first programmer
start reading its the code and look for `if', he will be expecting for blank
lines before its if\s. But will lose some time searching until realize
another programmer does not put them, or perhaps he forgot to insert them.
\cite{quantifyingProgramComprehension}

These differences are due to the diversity of ways we learn programming,
i.e., to the ways we are used to doing coding, as much as the abilities and
objectives of every programmer developed. Hence, nowadays it becomes a big
problem because we increasingly need more and more programmers working
together developing several and diverse computing systems. Where the latter
is due to the fact of the complexity of computer systems growing
increasingly, therefore over requiring programmers working and sharing their
codes and ideas. \cite{howProgrammersRead}

Moreover besides only worrying about how the code is displayed on their
computer screen, we need to worry about on how it will be saved in the file
system on its `plain-text' mode. Since for code sharing, it is vital for you
to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
which enable project manager\s and
programmers themselves, take control of their code changes
\cite{redesignOfGit}. It does allow to easily perform the tracking of code
changes \cite{gettingProductive} and
allow you to better understand what each programmer is doing
every time he formalizes a change in the code through a `commit', as in
`git' systems for example. \cite{usingSourceControl}

\begin{citacao}
I'd say there are two main reasons to enforce a single code format in a project. First has
to do with version control: with everybody formatting the code identically, all changes in
the files are guaranteed to be meaningful. No more just adding or removing a space here or
there, let alone reformatting an entire file as a `side effect' of actually changing just a
line or two. \cite{Geukens}
\end{citacao}

That is because while working with a versioning system like `git', we need
to keep the code among a single style or which we may call a `good practice'
set as standard for everybody, due the fact of letting each programmer to
write as he pleases, there will be plenty of noise on the code review and we
are figuring out what actually each programmer did \cite{quitDiffCalculating}.
Hence, if every programmer re-writes the history making changes
like inserting new lines
before each if, we end up with too much noise and focus of a versioning
system is to look at only those changes that are significant to the code,
such as the creation of new functions and not the addition of new blank
lines. \cite{findingRegressionsInProjects}

Talking about the last ideia pointed out, we could also think about an
approach to creating a new version control system which focuses only on
significant changes to the code, while reviewing code changes. However, this
approach could not be ideal, as for example, it would allow programmers to
start tedious wars of unproductive code adjustments. For example, imagine
how it would be for your every day and have to go through your code
re-adding new lines before each one of your beloved if\s, just because some
night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
had just removed them?

@@

Beforehand due the scope limitation for a Graduation Thesis,
we should only think about a basic, simple,
and yet reusable core of features.

\begin{enumerate}
    \item A Software Product with a great Object Orientation and possibilities of extension of features,
    decent research on the state of the art.

    \item Ranking all code formatting classes (beautifying) applicable.
    Including a study on what does is source beautifying,
    how to do such and why.

    \item Establish relationships between good programming practices and efficiency in programming,
    in addition to a new tool to support programmers in order to automate the long and diverse
    programming process in teams of developers with different programming `best practices'.

    \item Define, determine and classify which one are good programming practices and
    perform an in-depth study on the good practices on visual layout area,
    also known as code `Beautifying'.

    \item The definition of a flow pattern of development allowing teams of
    developers with different programming best practices,
    to work without intervene with each other up to start wars of `best good practices'.

    \item Discourse on the variety of existing tools for the support of good programming practices,
    with a comparative analysis between them,
    determining their weaknesses and strengths.
\end{enumerate}

@@

Propose a unique tool that allowing several and distinct
programming `best practices' being implemented in several programming
languages, which can be configured and set accordingly to their wishes,
from a single software working well behaved across all programming languages.

Moreover, explain the differences for other softwares and the benefits
of a unique tool, instead of several heavily different ones.

From this point, a sketch is presented on the problem, solutions,
information as for why to want make such software, or even why do we want to
beautifying things:

\begin{enumerate}[leftmargin=*]
    \item There are many different tools, sometimes paid, and difficult to
          complete. \cite{universalCodeFormatter}

    \item Many programming languages exist, so always having Beautifier
          software for each of them is very laborious
          \cite{universalCodeFormatter}. But the approach to a Universal
          Beautifier proposed in this work, would allow easily new languages to be
          added, being completely different from previous ones, or alike. And in
          case of similarities between them, it is enough to reuse their
          configuration structures already implemented.

    \item Looking for a Beautifier for each one of them because programmers
          currently work daily with several of these languages, and they are not
          similar. So you need to configure several beautifiers to do the
          formatting. This is a problem because only a few beautifiers are more
          complete, and every time you need to make a change in the formatting
          style, you must manually propagate the same change over several
          different program configuration files, which is bad because it takes the
          user a lot of time to learn how to handle many different types of
          settings. \cite{Schweitzer}

    \item In the case of ideal Beautifier, a change in your styling is
          propagated to all languages. And if you want to leave some language out
          of it, you just need to remove it from the list on which the
          configuration block applies to, and `a)' leave it out so no change is
          applied to. Or `b)' create a new block including only the block within
          the desired settings.

\end{enumerate}

The difference from this proposal to remaining formatting tools,
is the tradeoff between end\hyp{}users and developers responsibilities.
Most tools rarely expose to end\hyp{}users their language syntax specification,
in contrast,
this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
not requiring the tool to know any language syntax neither semantics.
Moreover,
with no syntax knowledge required,
the tool be can used with any languages their user wishes to.

>>>>

\lang{%
    The work first part will be based on research in
    articles, books, theses, dissertations, trusted authors websites,
    and through new demonstrated evidences based on arguments
    in the monograph evolution.
    Also, present results after building a new tool
    which proposes a solution for the problems presented and detailed.
}{%
    A \hyperref[sec:primeira_parte]{primeira parte} deste trabalho será baseado em artigos,
    livros, outras dissertações,
    sites confiáveis e por novas evidências demonstradas no desenvolvimento deste trabalho.
}

\lang{%
    In this proposal last chapter which lies on the part
    called `\nameref{sec:segunda_parte}', which holds the implementation of a
    tool for code `Beautifying'.
}{%
    E finalmente,
    na \hyperref[sec:segunda_parte]{segunda parte} deste trabalho,
    será apresentada a sugestão e implementação de uma ferramenta.
}

@@

\lang{%
    Questions like ``What are good programming practices?'' Or ``Why are these
    practices are good?''Are not easy to answer. But each programmer learns to
    write their codes in a certain way, with certain features like using 4 or 8
    spaces to indent lines, always leave a blank line before each control
    structure as if or for statements, and alike rules.
    \cite{naturalCodingConventions}
}{%
    Perguntas como ``O quê são boas práticas de programação'' não são fáceis de responder.
    Cada programador aprende a escrever seu códigos de uma determinada maneira,
    seja utilizando 2, 4,
    ou 8 espaços para criar blocos de indentação,
    ou sempre deixar uma linha em branco antes de estruturas de controle como if\s,
    while\s, etc. \cite{naturalCodingConventions}
}

\lang{%
    But entering the universe of good practices, there are many things for
    discoursing. Nonetheless, in this work is presented the implementation of
    tool called `Object Beautifier', which specifically dedicates on how to
    perform the best layout/display of programming code on the computer screen,
    so that maximize and facilitate the understanding of same
    \cite{automaticSynthesis}.
    Therefore, allowing the programmer to disperse
    more time and efforts thinking about its coding algorithms problem,
    other than trying to decipher the information that is presented
    to it on the screen through infinit different code layouts
    \cite{usingVersionControlData}.
}{%
    Assim,
    este trabalho será focado nas ferramentas disposição ou organização do código,
    também conhecidos como ``Source Code Beautifiers'' ou ``Formatadores de Código''.
    Com isso,
    espera\hyp{}se que o desenvolvimento de códigos demande menos esforços,
    pois o desenvolvedor pode forcar seus esforços pensando mais sobre o problema que está sendo resolvido,
    ao contrário de tentar decifrar o que está escrito em sua frente por meio
    de layouts extravagantes ou incomuns \cite{usingVersionControlData}.
}

\lang{%
    Within this work\s area, we need to also think long and hard about how to
    share the programming code of the programmers among you. Now, the problem of
    human diversity, like all big scientific questions -- how do you explain
    something like that -- It can be broken down into sub-questions. It happens
    many times, which is a good practice for a `Programmer A', is not the same
    to another `Programmer B'. For example, imagine some code where a programmer
    decided to put before each `if' statement, a blank line. It is therefore
    expected that whenever we see a blank line we can potentially find a
    matching `if', which can be considered a quite useful pattern matching as
    empty line may call better your attention. \cite{aPrettyGoodFormatting}
}{%
    Programação de computadores usualmente não é uma tarefa solitária.
    Muitos projetos podem sempre ser escritos pela mesma pessoa durante toda a vide desse projeto mas,
    o quão grande pode ser um projeto que uma pessoa pode fazer sozinha?
    Poderia uma pessoa escrever sozinha todo o sistema de controle de tráfego aéreo do Estados Unidos?
    Uma vez que precisa-se escrever sistemas computacionais maiores,
    tende-se a colocar vários programadores,
    engenheiros de software, gerentes de projeto, etc,
    para que se possa escrever o sistema computacional requerido
    entro do prazo que dado projeto computacional possui.

    Uma vez que isso acontece,
    como essas pessoas todas poderiam trabalhar juntas,
    mesmo elas não tendo o mesmo background?
    Assim,
    uma barreira extra para cada um desses programadores ao desenvolvimento do projeto será
    aprender as diferenças de trabalho que cada um desses desenvolvedores possuem entre sí.
    Uma das diferenças é a maneira no qual cada programador organiza
    estrutura de seu código no requisito de formatação.
    Por exemplo,
    imagine que um certo `Programador A' tem o costume de deixar uma linha
    em branco antes de cada estrutura de controle do tipo `if',
    `for',
    etc.
    Já um outro `Programador B',
    possui o costume oposto,
    ele jamais deixa uma linha em branco antes dessas estruturas de controle.
    Então,
    o quê pode dar de errado quando ambos os programadores `A' e `B' trabalham num mesmo projeto?

    Existem algumas possibilidades,
    uma delas poderia ser que a metade do código escrita pelo `Programador A' estará de um jeito.
    Já a outra metade escrita pelo `Programador B' estará de outro.
    Então,
    que tipos de problema isso poderia causar?
    Uma vez que o código não está mais todo escrito sobre um mesmo padrão,
    certas heurísticas perdem possuem sua taxa de acerto reduzidas ao fazer o reconhecimento de padrões.
    Um exemplo de padrão poderia ser rapidamente identificar onde pode estar uma estrutura de controle
    como `if' ou `for' de acordo com a presença ou não de uma linha em branco antes dela,
    já que a presença de uma linha em branco faz um destacamento maior sendo
    reconhecida como um separador de blocos de código distintos.
    \cite{aPrettyGoodFormatting}.
}

\lang{%
    But again this is something heavily dependent of what each one learning
    through their life time. Imagine another programmer do not liked this rule,
    and when he was writing your code involving an `if', he did not put such
    blank line another programmer is expecting. So when the first programmer
    start reading its the code and look for `if', he will be expecting for blank
    lines before its if\s. But will lose some time searching until realize
    another programmer does not put them, or perhaps he forgot to insert them.
    \cite{quantifyingProgramComprehension}
}{%

}

\lang{%
    These differences are due to the diversity of ways we learn programming,
    i.e., to the ways we are used to doing coding, as much as the abilities and
    objectives of every programmer developed. Hence, nowadays it becomes a big
    problem because we increasingly need more and more programmers working
    together developing several and diverse computing systems. Where the latter
    is due to the fact of the complexity of computer systems growing
    increasingly, therefore over requiring programmers working and sharing their
    codes and ideas. \cite{howProgrammersRead}
}{%

}

\lang{%
    Moreover besides only worrying about how the code is displayed on their
    computer screen, we need to worry about on how it will be saved in the file
    system on its `plain-text' mode. Since for code sharing, it is vital for you
    to use a versioning control system\footnote{\url{http://www.codeservedcold.com/version-control-importance/}}
    which enable project manager\s and
    programmers themselves, take control of their code changes
    \cite{redesignOfGit}. It does allow to easily perform the tracking of code
    changes \cite{gettingProductive} and
    allow you to better understand what each programmer is doing
    every time he formalizes a change in the code through a `commit', as in
    `git' systems for example. \cite{usingSourceControl}
}{%

}

\begin{citacao}
\lang{%
    I'd say there are two main reasons to enforce a single code format in a project. First has
    to do with version control: with everybody formatting the code identically, all changes in
    the files are guaranteed to be meaningful. No more just adding or removing a space here or
    there, let alone reformatting an entire file as a `side effect' of actually changing just a
    line or two. \cite{Geukens}
}{%

}
\end{citacao}

\lang{%
    That is because while working with a versioning system like `git', we need
    to keep the code among a single style or which we may call a `good practice'
    set as standard for everybody, due the fact of letting each programmer to
    write as he pleases, there will be plenty of noise on the code review and we
    are figuring out what actually each programmer did \cite{quitDiffCalculating}.
    Hence, if every programmer re-writes the history making changes
    like inserting new lines
    before each if, we end up with too much noise and focus of a versioning
    system is to look at only those changes that are significant to the code,
    such as the creation of new functions and not the addition of new blank
    lines. \cite{findingRegressionsInProjects}
}{%

}

\lang{%
    Talking about the last ideia pointed out, we could also think about an
    approach to creating a new version control system which focuses only on
    significant changes to the code, while reviewing code changes. However, this
    approach could not be ideal, as for example, it would allow programmers to
    start tedious wars of unproductive code adjustments. For example, imagine
    how it would be for your every day and have to go through your code
    re-adding new lines before each one of your beloved if\s, just because some
    night shift programmer\footnote{\url{https://blog.codinghorror.com/who-wrote-this-crap/}}
    had just removed them?
}{%

}

@@

\lang{%
    Beforehand due the scope limitation for a Graduation Thesis,
    we should only think about a basic, simple,
    and yet reusable core of features.
}{%

}

\begin{enumerate}
    \item
    \lang{%
        A Software Product with a great Object Orientation and possibilities of extension of features,
        decent research on the state of the art.
    }{%

    }
    \item
    \lang{%
        Ranking all code formatting classes (beautifying) applicable.
        Including a study on what does is source beautifying,
        how to do such and why.
    }{%

    }
    \item
    \lang{%
        Establish relationships between good programming practices and efficiency in programming,
        in addition to a new tool to support programmers in order to automate the long and diverse
        programming process in teams of developers with different programming `best practices'.
    }{%

    }
    \item
    \lang{%
        Define, determine and classify which one are good programming practices and
        perform an in-depth study on the good practices on visual layout area,
        also known as code `Beautifying'.
    }{%

    }
    \item
    \lang{%
        The definition of a flow pattern of development allowing teams of
        developers with different programming best practices,
        to work without intervene with each other up to start wars of `best good practices'.
    }{%

    }
    \item
    \lang{%
        Discourse on the variety of existing tools for the support of good programming practices,
        with a comparative analysis between them,
        determining their weaknesses and strengths.
    }{%

    }
\end{enumerate}

@@

\lang{%
    Propose a unique tool that allowing several and distinct
    programming `best practices' being implemented in several programming
    languages, which can be configured and set accordingly to their wishes,
    from a single software working well behaved across all programming languages.
}{%

}

\lang{%
    Moreover, explain the differences for other softwares and the benefits
    of a unique tool, instead of several heavily different ones.
}{%

}

\lang{%
    From this point, a sketch is presented on the problem, solutions,
    information as for why to want make such software, or even why do we want to
    beautifying things:
}{%

}

\begin{enumerate}[leftmargin=*]
    \item
    \lang{%
        There are many different tools, sometimes paid, and difficult to
        complete. \cite{universalCodeFormatter}
    }{%

    }
    \item
    \lang{%
        Many programming languages exist, so always having Beautifier
        software for each of them is very laborious
        \cite{universalCodeFormatter}. But the approach to a Universal
        Beautifier proposed in this work, would allow easily new languages to be
        added, being completely different from previous ones, or alike. And in
        case of similarities between them, it is enough to reuse their
        configuration structures already implemented.
    }{%

    }
    \item
    \lang{%
        Looking for a Beautifier for each one of them because programmers
        currently work daily with several of these languages, and they are not
        similar. So you need to configure several beautifiers to do the
        formatting. This is a problem because only a few beautifiers are more
        complete, and every time you need to make a change in the formatting
        style, you must manually propagate the same change over several
        different program configuration files, which is bad because it takes the
        user a lot of time to learn how to handle many different types of
        settings. \cite{Schweitzer}
    }{%

    }
    \item
    \lang{%
        In the case of ideal Beautifier, a change in your styling is
        propagated to all languages. And if you want to leave some language out
        of it, you just need to remove it from the list on which the
        configuration block applies to, and `a)' leave it out so no change is
        applied to. Or `b)' create a new block including only the block within
        the desired settings.
    }{%

    }
\end{enumerate}

\lang{%
    The difference from this proposal to remaining formatting tools,
    is the tradeoff between end\hyp{}users and developers responsibilities.
    Most tools rarely expose to end\hyp{}users their language syntax specification,
    in contrast,
    this proposal completely exposes the language to the end\hyp{}user as simple plain\hyp{}text,
    not requiring the tool to know any language syntax neither semantics.
    Moreover,
    with no syntax knowledge required,
    the tool be can used with any languages their user wishes to.
}{%

}

### 2019-04-22 monograph/thesis/chapters/motivation.tex
Removed the template monograph/thesis/postexto/apendice_a.tex
Fully inserted \lang tags on introduction.tex and motivation.tex

    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time \cite{howNovicesRead}.
    You expect:

    \begin{enumerate}
        \item Things to be well organized,
              so you do not get lost.
        \item The colors to be properly placed,
              so you do not get distracted from the main content.
        \item The spacing between paragraphs, words, chapters, sections
              subsections, etc, to be well adjusted.
              Not everything cluttered in only one file,
              line, function, class, or whatsoever so.
    \end{enumerate}

@@

    Your computer should help you with with these unforeseen tasks.
    Why should I spend my precious time checking whether I am actually copying
    something space indented,
    when I am actually coping something tab indented?

    Therefore, how to do such a thing on this 21\q{}st century?
    Perhaps we should sit and cry while waiting for some greater force to come
    and rescue us. Or may be you should stop crying and actually do something
    about other than keep waiting for you mommy to come and save you from the
    darkness growing behind you back leading you to endless unsleepy nights
    fixing your code just because everything just went wrong.

@@

    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:

    \begin{enumerate}[nosep,nolistsep]
        \item Add spaces before if\s name as in `if(var)' versus `if (var)'
        \item Add spaces inside if\s as in `if(var)' versus `if( var )'
        \item Add spaces before for\s name as in `for(var)' versus `for (var)'
        \item Add spaces inside for\s as in `for(var)' versus `for( var )'
        \item ...
    \end{enumerate}

    As may be noticed, the list may became quite big,
    and if fact such big list of rules has been implemented.
    Looking over the Beautifier called
    `Uncrustify'\footnote{\url{https://github.com/uncrustify/uncrustify}},
    we can find about 500 settings with specifications like these above.

    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.

>>>>

\lang{%
    Coding is like writing and reading a book for the large people, you like it
    to look beautifully. Or at least do you expect such when you buy a book, for
    example, to learn programming for you first time \cite{howNovicesRead}.
    You expect:
}{%

}

\begin{enumerate}
    \item
    \lang{%
        Things to be well organized,
        so you do not get lost.
    }{%

    }
    \item
    \lang{%
        The colors to be properly placed,
        so you do not get distracted from the main content.
    }{%

    }
    \item
    \lang{%
        The spacing between paragraphs, words, chapters, sections
        subsections, etc, to be well adjusted.
        Not everything cluttered in only one file,
        line, function, class, or whatsoever so.
    }{%

    }
\end{enumerate}

@@

\lang{%
    Your computer should help you with with these unforeseen tasks.
    Why should I spend my precious time checking whether I am actually copying
    something space indented,
    when I am actually coping something tab indented?
}{%

}

\lang{%
    Therefore, how to do such a thing on this 21\q{}st century?
    Perhaps we should sit and cry while waiting for some greater force to come
    and rescue us. Or may be you should stop crying and actually do something
    about other than keep waiting for you mommy to come and save you from the
    darkness growing behind you back leading you to endless unsleepy nights
    fixing your code just because everything just went wrong.
}{%

}

@@

\lang{%
    A robust Code Beautifier can get a lot more complicated just with the basic
    definitions of formatting (\nameref{source_code_beautifiers})
    applied over each language own characteristics
    as for example:
}{%

}

\begin{enumerate}[nosep,nolistsep]
    \item
    \lang{%
        Add spaces before if\s name as in `if(var)' versus `if (var)'
    }{%

    }
    \item
    \lang{%
        Add spaces inside if\s as in `if(var)' versus `if( var )'
    }{%

    }
    \item
    \lang{%
        Add spaces before for\s name as in `for(var)' versus `for (var)'
    }{%

    }
    \item
    \lang{%
        Add spaces inside for\s as in `for(var)' versus `for( var )'
    }{%

    }
\end{enumerate}

\lang{%
    As may be noticed, the list may became quite big,
    and if fact such big list of rules has been implemented.
    Looking over the Beautifier called
    `Uncrustify'\footnote{\url{https://github.com/uncrustify/uncrustify}},
    we can find about 500 settings with specifications like these above.
}{%

}

\lang{%
    The problem about is, even if you go through all these settings,
    which will take you quite some time,
    you still only configuring a few languages closely related.
    On this case, C, C++, Java, Pawn, etc.
    For all other languages you still need to find out another source code
    formatter tool, which will be certainly
    limited\footnote{\url{https://stackoverflow.com/questions/31438377/how-can-i-get-eclipse-to-wrap-lines-after-a-period-instead-of-before}}
    and still need to configure all over again.
}{%

}
